---
title: CV
author: Taras Kaduk
date: "`r format(Sys.time(), '%Y-%m-%d')`"
slug: cv
---

```{r setup, include=FALSE}
library(tidyverse)
library(stringr)
library(lubridate)
library(ggrepel)
library(readxl)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE)
```


### Summary

* Love R
* Love data science
* Love online learning, self-education, love spreading knowledge, love helping people learn stuff
* Hate redundancy, bad processes, manual tasks that should have been automated.
* Living a minimalism-driven and adventurous life, preferring flexibility and ability to move to new places or work remotely

### Mad R Skills
* tidyverse
* forecast
* caret
* rmarkdown

### Other rad skills
* SQL
* Power BI
* Data Visualization
* All things data

### Languages:
* Russian - native
* Ukrainian - native
* English - fluent
* French - elementary to intermediate

---

## Main Work Experience

### Manager, Business Intelligence & CRM
**Suddath**  |  April 2017 - Present  |  _Jacksonville, FL_

* Managing Business Intelligence at the Suddath Companies, overseeing retrospective analytics via Microsoft Power BI, planning next steps in company's analytics strategy.
* Started predictive analytics initiatives using R.
* Leading various analysts throughout all business units by providing guidance on data strategy, giving training and helping solve problems
* In charge of CRM adoption, usage and reporting on an enterprise level.

### Business Intelligence Analyst, Financial Planning & Analytics
**Suddath**  |  Jan 2017 - April 2017  |  _Jacksonville, FL_

* Continued providing Business Intelligence solutions on a larger scope
* Centralized, simplified, standardized and scaled most of the existing reports
* Provided training and guidance on Microsoft Power BI and working with data in general to other analysts in the organization.
* Crafted the analytics strategy for the enterprise

### Data Analyst,  Financial Planning & Analytics
**Suddath**  |  Oct 2015 - Jan 2017  |  _Seattle, WA_

* Piloted company's efforts on centralized retrospective analytics, migrated various reports from different sources into the enterprise's BI tool - Microsoft Power BI
* Acted as an SME for Power BI.

### Jr. Analyst, Decision Support
**Suddath**  |  Oct 2013 - Aug 2014  |  _Jacksonville FL_

* Ran and maintained reporting for the International line of business of the company via Microsoft Access
* Consolidated all reporting needs into one place, and optimized all recurring reports to run automatically.



```{r load, include=FALSE}
url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTabJ1NhzJ_D91_KsYz-DJqmfcRXNFskkQiJfwhwVvCImeTnLsoBRLahubWxNFVChZGd5HKbbRaG9bI/pub?output=xlsx"
destfile <- "data.xlsx"
curl::curl_download(url, destfile)
work <- read_xlsx(destfile, sheet = 'work') %>% 
        mutate(date_start = as.Date(date_start),
               date_end = as.Date(date_end),
               connect_to = as.Date(connect_to))


work <- work %>% 
  mutate(date_end2 = if_else(is.na(date_end), today(), date_end),
         duration = date_end2 - date_start) %>% 
  group_by(company) %>% 
  mutate(duration_company = cumsum(as.numeric(duration)),
         highlight_company = as.character(sum(is.na(date_end)))) %>% 
  ungroup() 

work_disp <- work %>% 
  select(start = date_start,
         end = date_end,
         title,
         company,
         employment = emp_type) %>% 
  arrange(desc(start))

work_comp <- work %>% 
  group_by(company) %>% 
  summarise(date_start = min(date_start),
            date_end = max(date_end),
            date_end2 = max(date_end2),
            duration_full = date_end2 - date_start)
```

### Full Work History... in a table
```{r table, echo=FALSE, out.width = '100%'}
knitr::kable(
  work_disp, format = 'markdown', padding = 0)
```

```{r graph_company, echo=FALSE, message=FALSE, warning=FALSE, fig.align = "center", out.width = '100%'}
ggplot(work) +
  geom_point(aes(x= date_start, y = duration_company - duration, col = highlight_company)) +
  geom_point(aes(x = date_end2, y = duration_company, col = highlight_company)) +
  geom_segment(aes(x=date_start, 
                   xend = date_end2, 
                   y = duration_company - duration, 
                   yend = duration_company, 
                   col = highlight_company),
               size = 1,
               alpha = 0.5) +
  geom_segment(aes(x=date_start, xend = date_end2, y = 0, yend = 0), alpha = 0.3, size = 10) +
  geom_text_repel(aes(x = date_end2, 
                      y = duration_company, 
                      label = title, 
                      vjust = 1, 
                      hjust = 0, 
                      col = highlight_company),
            size = 2,
            nudge_x = 10
            ) +
  geom_vline(xintercept = today(), linetype = 3, col = "#1a9641") +
  geom_text(aes(x = today(), y = 1300), label = 'Today', size = 3, vjust = -0.5, hjust = 0, col = '#1a9641', angle = 90) +
  geom_text(
    data = work_comp,
    aes(y = -50, 
        x = date_start, 
        label = company,
        hjust = 0), 
    size = 2) +
  theme_minimal() +
  scale_color_manual(name = "", values = c("grey40", "grey10")) +
  scale_size_manual(name = "", values = c(2, 3)) +
  scale_x_date(date_breaks = '1 year', date_labels = "%Y") +
  xlab('Timeline') +
  ylab('Career path duration') +
  theme(
    axis.text.y=element_blank(),
    axis.line.y = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position="none"
  ) +
  coord_equal()

```


## Education
### Kyiv National Economics University
2005 - 2008^[If you do the math right, you'll see that's not enough years to graduate. But you will also see that my first full-time job started while I was in school. Life took an unexpected turn, and I had to forget about school and start working. In part, this is why I believe in power of online education and self-learning: self-education is how I stay relevant]  |  Economics and Computer Science^[In Ukraine, there are no majors and minors in a way they exist in the US. Instead, bachelor degrees are somewhat predefined. Mine was called "Intellectual systems on decision making in economics and business". In reality, it was just a lot of Economics and Computer Science.]


### Self-education, online learning, MOOCs etc.
* DataCamp^[https://www.datacamp.com/profile/taraas] member since 2015, 130,000+ XP earned, 30+ courses completed
* Coursera^[https://www.coursera.org/user/318cf4331c68605ae73b4c3760d6d3da] and edX^[https://courses.edx.org/u/taraskaduk] member since 2013, auditing many classes and completing several.
* Active user on Duolingo^[https://www.duolingo.com/imtaraas] and Khan Academy^[https://www.khanacademy.org/profile/Taraas/], occasional user on Udacity, Udemy, FutureLearn, Memrise etc.


