---
title: Taras Kaduk
author: Resume
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[CO,CE]{CV is created using R language with rmarkdown and generated on `r Sys.Date()`}
output: tint::tintPdf
link-citations: yes
---

```{r setup, include=FALSE}
library(tidyverse)
library(stringr)
library(lubridate)
library(ggrepel)
library(readxl)
library(tint)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tint'))
options(htmltools.dir.version = FALSE)
```

```{marginfigure}
# Contact

* Phone: 425-524-2251
* Email: taras.kaduk@gmail.com
* Current location: Jacksonville, FL
* LinkedIn: [taraskaduk](https://www.linkedin.com/in/taraskaduk/)
* Twitter: [`@taraskaduk`](https://twitter.com/taraskaduk)
* Website: https://taraskaduk.com

# Summary
I am fond of data and love using it at work and outside of work to solve problems, make decisions, improve lives or just for fun. I hate redundancy and bad processes, love streamlining and automating all these manual things we humans shouldn't be doing. 
What I bring to the team is a fresh point of view, a desire to learn fast and to pass it on, an ability to communicate things well, a steady flow of asking "Why?", a diverse background, a funny accent, and some positive mental attitude to match.

# Objectives
* Looking for a company with a high degree of trust in its employees
* Will consider relocating
* Regardless of location, looking for a company where processes, policies and workflows support remote and flexible work.
* Well positioned and equally interested to be a senior IC, a team lead or a manager of a small team.


# Tools
* **SQL**: 6 years
* **R**: 4 years
* **Power BI**: 4 years
* **Tableau**: 1 year

# Areas of expertise:
* Web analytics & digital analytics
* Operations analytics (labor workforce, logistics etc)
* Financial reporting and analytics
* Management

# Languages:
* Russian - native
* Ukrainian - native
* English - fluent
* French - intermediate
```


# Key Work Experience

## Senior Digital Data Analyst
**TIAA Bank**  |  April 2018 - Present  |  _Jacksonville, FL_

* Processing data from web traffic and digital products use from its raw state to insights for stakeholders.
* Working on re-tagging of the bank website for better clickstream insights.
* Building out a reporting database: writing queries, ETL, documentation.
* Pioneering the adoption of R on the team. SME for R on the team.
* Toolset: SQL, R and Tableau.


## Manager, Data & Analytics
**Suddath**  |  April 2017 - April 2018 |  _Jacksonville, FL_

* Managed Data & Analytics at the Suddath Companies, overseeing retrospective analytics via Microsoft Power BI
* Started predictive analytics initiatives in the company using R.
* Worked with engineering team on creating a company-wide data warehouse.
* In charge of CRM adoption, usage and reporting on an enterprise level.

## Data Analyst,  Financial Planning & Analytics
**Suddath**  |  Oct 2015 - Apr 2017  |  _Remote_

* Piloted company's efforts on centralized retrospective analytics, migrated various reports from different sources into Microsoft Power BI
* Provided training and guidance on Microsoft Power BI and working with data in general to other analysts in the organization.
* Acted as the SME for Power BI.

## Jr. Data Analyst, Decision Support
**Suddath**  |  Oct 2013 - Aug 2014  |  _Jacksonville FL_

* Ran and maintained reporting for the International division via MS Access
* Consolidated, optimized and automated all existing reporting.



```{r load, eval=FALSE, include=FALSE}
# url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vTabJ1NhzJ_D91_KsYz-DJqmfcRXNFskkQiJfwhwVvCImeTnLsoBRLahubWxNFVChZGd5HKbbRaG9bI/pub?output=xlsx"
# destfile <- "data.xlsx"
# curl::curl_download(url, destfile)
# work <- read_xlsx(destfile, sheet = 'work') %>% 
#         mutate(date_start = as.Date(date_start),
#                date_end = as.Date(date_end),
#                connect_to = as.Date(connect_to))

work <- read_csv("cv.csv") %>% 
        mutate(date_start = as.Date(date_start),
               date_end = as.Date(date_end),
               connect_to = as.Date(connect_to))


work <- work %>% 
  mutate(date_end2 = if_else(is.na(date_end), today(), date_end),
         duration = date_end2 - date_start) %>% 
  ungroup() %>% 
  group_by(company) %>% 
  mutate(duration_company = cumsum(as.numeric(duration)),
         highlight_company = as.character(sum(is.na(date_end)))) %>% 
  ungroup() 

work_disp <- work %>% 
  select(Start = date_start,
         End = date_end,
         Title = title,
         Company = company,
         Employment = emp_type,
         Location = location) %>% 
  arrange(desc(Start)) %>% 
  mutate(Start = format(Start, '%b %Y'),
         End = as.character(format(End, '%b %Y'))) %>% 
  replace_na(list(End = "Present"))

work_comp <- work %>% 
  group_by(company) %>% 
  summarise(date_start = min(date_start),
            date_end = max(date_end),
            date_end2 = max(date_end2),
            duration = date_end2 - date_start)
```

***


```{r table, fig.fullwidth=TRUE, eval = FALSE, include = FALSE}
# Full Work History
knitr::kable(work_disp)
```



# Education

## Kyiv National Economic University
2005 - 2009  |  Computer Science  |  _Kyiv, Ukraine_

## Self-education, online learning, MOOCs etc.
* DataCamp^[[https://www.datacamp.com/profile/taraskaduk](https://www.datacamp.com/profile/taraskaduk)] member since 2015, "Data Analyst with R" and "Data Scientist with R" tracks completed.
* Coursera^[[https://www.coursera.org/user/318cf4331c68605ae73b4c3760d6d3da](https://www.coursera.org/user/318cf4331c68605ae73b4c3760d6d3da)] and edX^[[https://courses.edx.org/u/taraskaduk](https://courses.edx.org/u/taraskaduk)] member since 2013, auditing many classes and completing several.
* Active user on Duolingo^[[https://www.duolingo.com/taraskaduk](https://www.duolingo.com/taraskaduk)] and Khan Academy^[[https://www.khanacademy.org/profile/taraskaduk/](https://www.khanacademy.org/profile/taraskaduk/)], occasional user on Udacity, Udemy, FutureLearn & Memrise.


